Studying the Performance of the Jellyfish Optimiser for the Application of Projection Pursuit

### 2024-05-30 optim.qmd
replace sim_sine_6d_dcor2d with smaller datasets

```{r}
load(here::here("data/sim_sine_6d_dcor2d.rda"))
```

```{r}
dplyr::glimpse(sim_sine_6d_dcor2d |> select(-id)) 
```

@@

```{r}
set.seed(123456)
sin1000 <- spinebil::sinData(6, 1000) %>% scale() %>% as_tibble()
colnames(sin1000) <- paste0("V", 1:6)

sine_dcor2d_5050 <- sim_sine_6d_dcor2d |> 
  filter(n_jellies == 50, max_tries == 50)
best_sim <-  sine_dcor2d_5050|> 
  group_by(sim) |> 
  filter(index_val == max(index_val)) |> 
  filter(row_number() == 1) 
proj_dt <- map_dfr(best_sim |> pull(basis), 
              ~as_tibble(as.matrix(sin1000) %*% .x), .id = "sim")

@@

```{r}
theo_best <- matrix(c(rep(0, 8), 1, 0, 0, 1), nrow = 6, byrow = TRUE)
angle_dcor2d <- sine_dcor2d_5050 |>
    rowwise() |>
    mutate(angle = tourr::proj_dist(theo_best, basis))

@@

```{r}
load(here::here("data/smoothness.rda"))
smoothness |> select(index, n, variance:nugget) |> knitr::kable(digits = 3)
load(here::here("data/squintability.rda"))
squintability |> knitr::kable(digits = 3)
```

>>>>

```{r}
load(here::here("data/sim_example.rda"))
```

```{r}
dplyr::glimpse(sim_example |> select(-id)) 
```

@@

```{r}
load(here::here("data/sine_dcor2d_best.rda"))
set.seed(123456)
sin1000 <- spinebil::sinData(6, 1000) %>% scale() %>% as_tibble()
colnames(sin1000) <- paste0("V", 1:6)

proj_dt <- map_dfr(sine_dcor2d_best |> pull(basis), 
              ~as_tibble(as.matrix(sin1000) %*% .x), .id = "sim")

@@

```{r eval = FALSE}
theo_best <- matrix(c(rep(0, 8), 1, 0, 0, 1), nrow = 6, byrow = TRUE)
angle_dcor2d <- sine_dcor2d_5050 |>
    rowwise() |>
    mutate(angle = tourr::proj_dist(theo_best, basis))

@@

```{r}
load(here::here("data/smoothness.rda"))
smoothness |> knitr::kable(digits = 3)
load(here::here("data/squintability.rda"))
squintability |> knitr::kable(digits = 3)
```

### 2024-05-30 optim.tex
replace sim_sine_6d_dcor2d with smaller datasets

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toptitle=1mm, toprule=.15mm, colback=white, colframe=quarto-callout-note-color-frame, arc=.35mm, breakable, leftrule=.75mm, opacitybacktitle=0.6, bottomtitle=1mm, titlerule=0mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, bottomrule=.15mm, left=2mm, opacityback=0]

@@

\begin{verbatim}
Rows: 275,000
Columns: 13
$ idx_f     <chr> "dcor2d_2", "dcor2d_2", "dcor2d_2", "dcor2d_2", "dcor2d_2", ~
$ d         <dbl> 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, ~
$ n_jellies <dbl> 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, 20, ~
$ max_tries <dbl> 50, 50, 50, 50, 50, 50, 50, 50, 50, 50, 50, 50, 50, 50, 50, ~
$ sim       <int> 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, ~
$ seed      <int> 3462, 3462, 3462, 3462, 3462, 3462, 3462, 3462, 3462, 3462, ~
$ basis     <list> <<matrix[6 x 2]>>, <<matrix[6 x 2]>>, <<matrix[6 x 2]>>, <<~
$ index_val <dbl> 0.0247212373, 0.0033938502, 0.0463398915, 0.0486230801, -0.0~
$ info      <chr> "initiation", "initiation", "initiation", "initiation", "ini~
$ method    <chr> "search_jellyfish", "search_jellyfish", "search_jellyfish", ~
$ tries     <dbl> 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, ~
$ loop      <dbl> 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 1~
$ time      <drtn> 35.46031 secs, 35.46031 secs, 35.46031 secs, 35.46031 secs,~
\end{verbatim}

@@

\begin{longtable}[]{@{}lrrrrr@{}}
\toprule\noalign{}
index & n & variance & range & smoothness & nugget \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
dcor2d\_2 & 6 & 0.034 & 0.167 & 2.663 & 0.114 \\
loess2d & 6 & 0.083 & 0.307 & 2.194 & 0.292 \\
MIC & 6 & 0.016 & 0.100 & 2.394 & 0.087 \\
TIC & 6 & 0.124 & 0.104 & 2.471 & 0.086 \\
stringy & 6 & 0.000 & 1173.035 & 1.031 & 17608.047 \\
splines2d & 6 & 0.040 & 0.189 & 2.606 & 0.104 \\
MIC & 8 & 0.016 & 0.100 & 2.394 & 0.087 \\
TIC & 8 & 0.124 & 0.104 & 2.471 & 0.086 \\
holes & 6 & 0.002 & 0.408 & 2.364 & 0.212 \\
holes & 8 & 0.000 & 0.259 & 2.373 & 0.613 \\
holes & 10 & 0.000 & 0.144 & 2.317 & 1.831 \\
holes & 12 & 0.000 & 0.254 & 2.173 & 0.879 \\
\end{longtable}

>>>>

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, coltitle=black, toptitle=1mm, toprule=.15mm, leftrule=.75mm, left=2mm, colback=white, opacitybacktitle=0.6, title={Algorithm: Jellyfish Optimizer Pseudo Code}, bottomtitle=1mm, rightrule=.15mm]

@@

\begin{verbatim}
Rows: 10
Columns: 13
$ idx_f     <chr> "dcor2d_2", "dcor2d_2", "dcor2d_2", "dcor2d_2", "dcor2d_2", ~
$ d         <dbl> 6, 6, 6, 6, 6, 6, 6, 6, 6, 6
$ n_jellies <dbl> 20, 20, 20, 20, 20, 20, 20, 20, 20, 20
$ max_tries <dbl> 50, 50, 50, 50, 50, 50, 50, 50, 50, 50
$ sim       <int> 1, 1, 1, 1, 1, 1, 1, 1, 1, 1
$ seed      <int> 3462, 3462, 3462, 3462, 3462, 3462, 3462, 3462, 3462, 3462
$ basis     <list> <<matrix[6 x 2]>>, <<matrix[6 x 2]>>, <<matrix[6 x 2]>>, <<m~
$ index_val <dbl> 0.0247212373, 0.0033938502, 0.0463398915, 0.0486230801, -0.0~
$ info      <chr> "initiation", "initiation", "initiation", "initiation", "ini~
$ method    <chr> "search_jellyfish", "search_jellyfish", "search_jellyfish", ~
$ tries     <dbl> 1, 1, 1, 1, 1, 1, 1, 1, 1, 1
$ loop      <dbl> 1, 2, 3, 4, 5, 6, 7, 8, 9, 10
$ time      <drtn> 35.46031 secs, 35.46031 secs, 35.46031 secs, 35.46031 secs, ~
\end{verbatim}

@@

\begin{longtable}[]{@{}lrrrrr@{}}
\toprule\noalign{}
index & n & variance & range & smoothness & nugget \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
holes & 6 & 0.002 & 0.408 & 2.364 & 0.212 \\
holes & 8 & 0.000 & 0.259 & 2.373 & 0.613 \\
holes & 10 & 0.000 & 0.144 & 2.317 & 1.831 \\
holes & 12 & 0.000 & 0.254 & 2.173 & 0.879 \\
MIC & 6 & 0.016 & 0.100 & 2.394 & 0.087 \\
MIC & 8 & 0.016 & 0.100 & 2.394 & 0.087 \\
TIC & 6 & 0.124 & 0.104 & 2.471 & 0.086 \\
TIC & 8 & 0.124 & 0.104 & 2.471 & 0.086 \\
dcor2d\_2 & 6 & 0.034 & 0.167 & 2.663 & 0.114 \\
loess2d & 6 & 0.083 & 0.307 & 2.194 & 0.292 \\
splines2d & 6 & 0.040 & 0.189 & 2.606 & 0.104 \\
stringy & 6 & 0.000 & 1173.035 & 1.031 & 17608.047 \\
\end{longtable}
